MNRAS \LaTeXe\ template -- title goes here

### 2017-10-27 Paper/paper.tex
some references, unexpected format

\cite{Tweb}.

@@

The evolution in time was performed with the hydrodynamic code AREPO
\cite{arepo}, which combines a moving Voronoi tessellation with the
finite volume approach. Included in the evolution algorithm, there are
galaxy formation models which account for the evolution of stars and
SMBHs. Specifically, the physics followed by this model includes
energetic feedback from supermassive black holes and supernovae, as
well as stellar evolution and chemical enrichment. This level of
detail in Illustris is advantageous for the analysis of the effect of
the environment in barionic properties of galaxies. This level of resolution is hard to find
among other simulations, i.e. post-processed runs with semi-analytical
models which do not directly simulate baryons.(Expand) Describe Arepo more\\

The output of this simultaion consists of 136 snapshots. 61 of
them were taken at $z < 3$ spaced with a cosmological scale factor
$\Delta a \approx 0.02$. The remaining 75 were taken at $z > 3$
with spacing $\Delta a \approx 0.01$. Each snapshot was post-processed
with a modified version of FOF \cite{FOF} to identify DM haloes with
more than 32 particles using a linking length of 0.2 times the mean
particle separation. Each output group from the 7,713,601 post-processed halos (FOF) is analyzed with the SUBFIND
algorithm \cite{subfind} to generate, at z=0,
and 4,366,546 (sub)halo catalogues with their respective
characterization properties. \\

@@

@@

Jones et al. \cite{jones1} the SDSS \cite{SDSS2011} catalogue to define the environment of galaxies in the ALFALFA \cite{ALFALFA} survey.
This SDSS catalogue was chosen to be optically-selected and volume-limited to account for apparent lonely galaxies in ALFALFA with increasinf distance. 
For this reason, they pre-selected galaxies brighter than $M_r = -18.9$ in this survey.

@@

As we want to replicate as closely as possible the method effectuated by Jones et. al \cite{jones1}, we use the same specifications to calculate the environment.
We perform the analysis of the Schechter functions to gas, DM, stellar and BH mass functions.
We do not perform the study directly on HIMFs because this would require some extense calculations. We take the gas mass function as a first approximation.\\

\subsubsection{The cosmic web method}
To complement and verify the analysis performed with the third nearest neighbor method, we chose a complementary method of completely different nature. 
The chosen method was developed by Forero et al. \cite{forero1}. 
It uses the Hessian \ref{eq:hessian} of the gravitational potential obtained from the DM density field to classify galaxies into four morphological environments.\\

@@

Specifically, we diagonalize the Hessian matrix obtaining three eigenvalues. 
These eigenvalues determine the concavity of the gravitational potential on the principal axes, at each point. We use these eigenvalues to interpret the tendence of mass to cluster with reference with some given threshold $\lambda$. 
Eigenvalues bigger than $\lambda$ are interpreted as a local tendence of mass to expand? in the respective eigenaxes, and viceversa. 
With this characterization, clusters, sheets, fillaments and voids can be defined with the number of axes above $\lambda$.
Forero et. al. found in \cite{forero2009} that the critical value that better reproduces the correct morphological pulations was $\lambda = 0.2$. \\

@@

% Example table
\begin{table}
	\centering
	\caption{This is an example table. Captions appear above each table.
	Remember to define the quantities, symbols and units used.}
	\label{tab:example_table}
	\begin{tabular}{lccr} % four columns, alignment for each
		\hline
		A & B & C & D\\
		\hline
		1 & 2 & 3 & 4\\
		2 & 4 & 6 & 8\\
		3 & 5 & 7 & 9\\
		\hline
	\end{tabular}
\end{table}

>>>>

\cite{Forero2009}.

@@

The evolution in time was performed with the hydrodynamic code AREPO
\cite{Arepo}, which combines a moving Voronoi tessellation with the
finite volume approach. Included in the evolution algorithm, there are
galaxy formation models which account for the evolution of stars and
SMBHs. Specifically, the physics followed by this model includes
energetic feedback from supermassive black holes and supernovae, as
well as stellar evolution and chemical enrichment. This level of
detail in Illustris is advantageous for the analysis of the effect of
the environment in barionic properties of galaxies. This level of resolution is hard to find
among other simulations, i.e. post-processed runs with semi-analytical
models which do not directly simulate baryons.(Expand) Describe Arepo more\\

The output of this simultaion consists of 136 snapshots. 61 of
them were taken at $z < 3$ spaced with a cosmological scale factor
$\Delta a \approx 0.02$. The remaining 75 were taken at $z > 3$
with spacing $\Delta a \approx 0.01$. Each snapshot was post-processed
with a modified version of FOF \cite{FOF} to identify DM haloes with
more than 32 particles using a linking length of 0.2 times the mean
particle separation. Each output group from the 7,713,601 post-processed halos (FOF) is analyzed with the SUBFIND
algorithm \cite{SUBFIND} to generate, at z=0,
and 4,366,546 (sub)halo catalogues with their respective
characterization properties. \\

@@

To obtain the Schechter parameters that characterize each numerical mass function, we used MCMC to obtain the fit with best likelihood. 
With this, we could also ...\\

\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{./pics/MassResolution.png}
    \caption{The effect on mass resolution on mass functions of Illustris-1,2,3. (Masses have units $10^{10}M_\odot$)} 
    \label{fig:resolution effects}
\end{figure}

@@

Jones et al. \cite{Jones2016} the SDSS \cite{SDSS2011} catalogue to define the environment of galaxies in the ALFALFA \cite{ALFALFA} survey.
This SDSS catalogue was chosen to be optically-selected and volume-limited to account for apparent lonely galaxies in ALFALFA with increasinf distance. 
For this reason, they pre-selected galaxies brighter than $M_r = -18.9$ in this survey.\\

@@

As we want to replicate as closely as possible the method effectuated by Jones et. al \cite{Jones2016}, we use the same specifications to calculate the environment.
We perform the analysis of the Schechter functions to gas, DM, stellar and BH mass functions.
We do not perform the study directly on HIMFs because this would require some extense calculations. We take the gas mass function as a first approximation.\\

\subsubsection{The cosmic web method}
To complement and verify the analysis performed with the third nearest neighbor method, we chose a complementary method of completely different nature. 
The chosen method was developed by Forero et al. \cite{Forero2009}. 
It uses the Hessian \ref{eq:hessian} of the gravitational potential obtained from the smoothened DM density field to classify galaxies into four morphological environments.\\

@@

Specifically, we diagonalize the Hessian matrix of the gravitational potential $\phi$ obtaining three eigenvalues. 
This matrix encodes the local curvature of the gravitational potential. 
Specifically, these eigenvalues determine the concavity of $\phi$ on the principal axes, at each point. 
We use these eigenvalues to interpret the tendence of mass to cluster with reference with some given threshold $\lambda$. 
Eigenvalues bigger than $\lambda$ are interpreted as a local tendence of mass to cluster in the respective eigenaxes, and viceversa. 
With this characterization, clusters, sheets, fillaments and voids can be defined with the number of eigenvalues above $\lambda$.
Forero et. al. found in \cite{forero2009} that the critical value that better reproduces the correct morphological populations was $\lambda = 0.2$. \\

@@
